---
title: "Personality Traits of Current and Future Accountants: Evidence from the Socio-Economic Panel"
author: "Ulf Brüggemann & Jonas Materna"
institute: "TRR 266 Accounting for Transparency"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: "9pt"
output: 
  beamer_presentation: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

        
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \input{beamer_theme_trr266.sty}
---


```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
library(tidyverse)
library(kableExtra)
load("../output/results.rda")



```


# Intro

### Short intro to the SOEP

   

# Big 5 Personality traits of Accountants
### Big 5 Personality traits of Accountants: Agreeableness
- Am sometimes too coarse with others   
- Able to forgive                      
- Friendly with others  


### Big 5 Personality Traits of Accountants (Control: Professionals)
``` {r tab_big5_1, results="asis"}
var_names <- var_names_big5
tab <- tab_big5_1$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:36],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```
### Big 5 Personality Traits of Accountants (Control: All)
``` {r tab_big5_2, results="asis"}
var_names <- var_names_big5
tab <- tab_big5_2$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:36],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```

### Satisfaction measures 
``` {r tab_sat_1, results="asis"}
var_names <- var_names_sat
tab <- tab_sat_1$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], "\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(3:15)],
  label = var_names$label[c(3:15)]
)
for (i in seq(15, 45, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:27],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Satisfaction measures 
``` {r tab_sat_2, results="asis"}
var_names <- var_names_sat_control_only
tab <- tab_sat_2$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], "\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(3:8)],
  label = var_names$label[c(3:8)]
)
for (i in seq(15, 30, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:42],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Satisfaction measures 
``` {r tab_sat_3, results="asis"}
var_names <- var_names_sat
tab <- tab_sat_3$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], "\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(3:13)],
  label = var_names$label[c(3:13)]
)
for (i in seq(15, 30, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:42],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))


``` 




### Determinants of job satisfaction


``` {r tab_sat_pid_FE, results="asis"}
var_names <- var_sat_pid_FE
tab <- tab_sat_pid_FE$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(2:5)],
  label = var_names$label[c(2:5)]
)
for (i in seq(14, 23, by = 3)) {
  pos <- (i-11)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:35],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```

# Appendix
``` {r draft, results="asis"}
latex_tab <- c(
  " \\begin{center}",
  " \\resizebox*{!}{0.8\\textheight}{",
  " \\begin{tabular}{lcccccc}",
 " \\\\[-1.8ex]\\hline "  ,                                                                                             
  " \\hline \\\\[-1.8ex] "    ,                                                                                          
 " & \\multicolumn{5}{c}{\\textit{Dependent variable:}} \\\\ "  ,                                                      
 " \\cline{2-6} "             ,                                                                                         
 " \\\\[-1.8ex] & Agreeableness & Conscientiousness & Extraversion & Neuroticism & Openness \\\\"  ,                    
 " \\\\[-1.8ex] & (1) & (2) & (3) & (4) & (5)\\\\ "                                                 ,                   
 " \\hline \\\\[-1.8ex] "  ,                                                                                            
 " Sample (1 = Accountant) & $-$0.108$^{**}$ & 0.082$^{*}$ & $-$0.022 & $-$0.248$^{***}$ & $-$0.133$^{**}$ \\\\ "  ,   
 "  & (0.049) & (0.045) & (0.060) & (0.063) & (0.064) \\\\ "                                                        ,  
"  & & & & & \\\\ "                                                                                                  ,
 " Gender (1 = Female) & 0.271$^{***}$ & 0.092$^{***}$ & 0.170$^{***}$ & 0.540$^{***}$ & 0.124$^{***}$ \\\\ "         ,
 "  & (0.007) & (0.007) & (0.009) & (0.009) & (0.010) \\\\ "                                                          ,
 "  & & & & & \\\\ "                                                                                                  ,
 " German (1 = True) & $-$0.471$^{***}$ & $-$0.307$^{***}$ & $-$0.208$^{***}$ & 0.033$^{**}$ & $-$0.299$^{***}$ \\\\ ",
"  & (0.011) & (0.010) & (0.014) & (0.014) & (0.014) \\\\ "                                                          ,
 "  & & & & & \\\\ "                                                                                                  ,
 " Constant & 5.733$^{***}$ & 5.965$^{***}$ & 5.024$^{***}$ & 3.467$^{***}$ & 4.834$^{***}$ \\\\ "                    ,
 "  & (0.011) & (0.010) & (0.013) & (0.014) & (0.014) \\\\ "                                                          ,
 "  & & & & & \\\\ "                                                                                                  ,
 "\\hline \\\\[-1.8ex] "                                                                                              ,
 "Estimator & ols & ols & ols & ols & ols \\\\ "                                                                      ,
 "Fixed effects & None & None & None & None & None \\\\ "                                                             ,
 "Std. errors clustered & No & No & No & No & No \\\\ "                                                               ,
 "Observations & 57,480 & 51,398 & 57,384 & 57,477 & 57,116 \\\\ "                                                    ,
 "$R^{2}$ & 0.050 & 0.019 & 0.010 & 0.054 & 0.010 \\\\ "                                                              ,
 "Adjusted $R^{2}$ & 0.050 & 0.019 & 0.010 & 0.054 & 0.010 \\\\ "                                                     ,
 "\\hline "                                                                                                           ,
 "\\hline \\\\[-1.8ex] "                                                                                              ,
 "\\textit{Note:}  & \\multicolumn{5}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\\\ " ,
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```
