---
title: "Personality Traits of Current and Future Accountants: Evidence from the Socio-Economic Panel"
author: "Ulf Brüggemann & Jonas Materna"
institute: "TRR 266 Accounting for Transparency"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: "9pt"
output: 
  beamer_presentation: 
    latex_engine: xelatex # pdflatex creates rastered fonts
    slide_level: 3

        
header-includes:
- \usepackage{booktabs} 
- \usepackage{threeparttable}
- \usepackage{graphicx}
- \input{beamer_theme_trr266.sty}
---


```{r setup, include=FALSE, cache=F, message=F, warning=F, results="hide"}
knitr::opts_chunk$set(
  cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE
)
library(tidyverse)
library(kableExtra)
load("../output/results_big5.rda")
load("../output/results_satisfaction.rda")
```


# Intro

### Short intro to the SOEP

- ...

# Who are the individuals that work in accounting?

### Big 5 Personality Traits of Accountants (Control: Professionals)
``` {r accountantsProfBig5, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_acc_prof_YearFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Satisfaction of Accountants (Control: Professionals)
``` {r accountantsProfSat_YearFE, results="asis"}
var_names <- var_names_accountants_sat
tab <- tab_accountant_job_sat_YearFE$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(5:10)],
  label = var_names$label[c(5:10)]
)
for (i in seq(15, 30, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```

# What happens after entering the accounting profession?

### Big 5 Personality Traits of Accountants (Control: Professionals)
``` {r accountantsProfBig5_PersonFE, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_acc_prof_PersonFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Satisfaction of Accountants (Control: Professionals)
``` {r accountantsProfSat_PersonFE, results="asis"}
var_names <- var_names_accountants_sat
tab <- tab_accountant_job_sat_PersonFE$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(5:10)],
  label = var_names$label[c(5:10)]
)
for (i in seq(15, 30, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```

# Appendix

### Big 5 Personality Traits of Accountants (Control: Highly Skilled Workers)
``` {r accountantsSkillBig5, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_acc_skill_YearFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```


### Big 5 Personality Traits of Accountants (Control: Highly Skilled Workers)
``` {r accountantsSkillBig5_PersonFE, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_acc_skill_PersonFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```




### Big 5 Personality Traits of Young Accountants (Control: Young Highly Skilled Workers)
``` {r accountantsYSkillBig5, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_yacc_yskill_YearFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```



### Big 5 Personality Traits of Young Accountants (Control: Young Highly Skilled Workers)
``` {r accountantsYSkillBig5_PersonFE, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_yacc_yskill_PersonFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```





### Big 5 Personality Traits of Accountants, Bookkeepers and Clerks (Control: Full time employed)
``` {r accountantsBookBig5_YearFE, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_book_lab_YearFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```



### Big 5 Personality Traits of Accountants, Bookkeepers and Clerks (Control: Full time employed)
``` {r accountantsBookBig5_PersonFE, results="asis"}
var_names <- var_names_accountants_big5
tab <- tab_book_lab_PersonFE_big5$table
tab[12] <- paste(
  "\\\\[-1.8ex] &", var_names$label[1], 
  "&", var_names$label[2], 
  "&", var_names$label[3], 
  "&", var_names$label[4],
  "&", var_names$label[5],"\\\\"
)
esc_var_names <- str_replace_all(var_names$var_name, fixed ("_"), "\\_")
reg_names <- tibble(
  var_name = esc_var_names[c(6:10)],
  label = var_names$label[c(6:10)]
)
for (i in seq(15, 27, by = 3)) {
  pos <- (i-12)/3
  tab[i] <- str_replace(
    tab[i], fixed(reg_names$var_name[pos]), reg_names$label[pos]
  )
}
latex_tab <- c(
  "\\begin{center}",
  "\\resizebox*{!}{0.8\\textheight}{",
  "\\begin{tabular}{lccccc}",
  tab[8:39],
  "\\end{tabular}}",
  "\\end{center}"
)
cat(paste(latex_tab, collapse = "\n"))
```